% --- Python Developer CV ---

\documentclass[letterpaper,11pt]{article}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Define custom colors
\definecolor{linkcolor}{HTML}{2b6cb0}
\definecolor{sectioncolor}{HTML}{1a365d}

% Configure hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    urlcolor=linkcolor,
}

% Custom section formatting
\titleformat{\section}
{\Large\bfseries\color{sectioncolor}}
{}{0em}
{\uppercase}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{4pt}

% Custom commands for entries
\newcommand{\resumeItem}[1]{\item #1}

\newcommand{\entryList}{\begin{itemize}[leftmargin=*,nosep]}
\newcommand{\entryListEnd}{\end{itemize}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
  \item[]
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}
  \vspace{-5pt}
}

% Fix for FontAwesome warnings - protect icons from becoming bold
\newcommand{\normalfaCalendar}{{\mdseries\faCalendar}}
\newcommand{\normalfaEnvelope}{{\mdseries\faEnvelope}}
\newcommand{\normalfaLinkedin}{{\mdseries\faLinkedin}}
\newcommand{\normalfaGithub}{{\mdseries\faGithub}}
\newcommand{\normalfaGlobe}{{\mdseries\faGlobe}}
\newcommand{\normalfaExternalLink}{{\mdseries\faExternalLink}}
\newcommand{\normalfaYoutube}{{\mdseries\faYoutube}}

\clubpenalty=1000
\widowpenalty=1000

\begin{document}

\begin{center}
\textbf{\Huge Alejandro Sánchez Yalí}\\[0.2em]
\textbf{\Large Python Developer | Full Stack Engineer}\\[0.4em]
\small
\normalfaCalendar\ \href{https://cal.com/asanchezyali/full-time-opportunities}{\textsc{Let's Connect}}

\vspace{0.8em}
\normalfaEnvelope\ \href{mailto:asanchezyali@gmail.com}{asanchezyali@gmail.com}  ~|~
\normalfaLinkedin\ \href{https://www.linkedin.com/in/asanchezyali}{asanchezyali} ~|~
\normalfaGithub\ \href{https://github.com/asanchezyali}{asanchezyali}  ~|~
\normalfaGlobe\ \href{https://asanchezyali.com}{asanchezyali.com}
\end{center}

\section{Summary}
Python Developer and Full Stack Engineer with 5+ years of experience building robust, scalable backend and frontend solutions. Strong mathematical background and hands-on expertise in Python for web development, data processing, and AI/ML integration. Proven track record delivering production-ready APIs, deploying machine learning models, and integrating modern frontend technologies. Experienced in cloud infrastructure, DevOps, and technical leadership.

\section{Technical Skills}
\begin{itemize}[leftmargin=*, itemsep=0pt]
  \item \textbf{Languages:} Python (advanced, 7+ years), JavaScript/TypeScript (5+ years), SQL, C, Rust
  \item \textbf{Backend:} Django, FastAPI, Flask, Node.js, RESTful APIs, GraphQL
  \item \textbf{Frontend:} React.js, Next.js, TypeScript
  \item \textbf{AI/ML:} TensorFlow, PyTorch, Scikit-learn, Pandas, NumPy, LangChain, LLMs, Whisper, JAX/Flax
  \item \textbf{Data Engineering:} ETL pipelines, data processing, web scraping (BeautifulSoup, ScrapeGraph, Selenium)
  \item \textbf{Databases:} PostgreSQL, MongoDB
  \item \textbf{Cloud/DevOps:} AWS, GCP, Docker, GitHub Actions, CI/CD pipelines
  \item \textbf{Software Engineering:} Clean Architecture, TDD, SOLID principles, Unit Testing, Version Control
\end{itemize}

\section{Experience}
\begin{itemize}[leftmargin=0pt, itemindent=0pt, label={}, itemsep=1pt]
\resumeSubheading
{Full Stack Developer}{Apr 2021 -- Aug 2024}
{Monadical}{Remote, Canada/US}
\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item Developed and maintained full-stack applications using Python (Django, FastAPI) and JavaScript / TypeScript (React.js, Next.js).
    \item Built scalable backend systems and RESTful APIs for AI/ML model deployment and data-intensive applications.
    \item Integrated large language models and AI services into production environments.
    \item Designed ETL pipelines and custom Django ORM extensions in Python.
    \item Created frontend interfaces for AI applications using React / Next.js and TypeScript.
\end{itemize}

\resumeSubheading
{Independent IT Consultant}{Aug 2024 -- Present}
{Freelance}{Remote}
\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item Delivered end-to-end software solutions for business applications using Python, FastAPI, Django, and React.js.
    \item Developed AI agents and technical English learning platforms leveraging Python and LLMs.
\end{itemize}

\resumeSubheading
{Full Stack Developer}{Aug 2018 -- Oct 2020}
{BCFort}{Medellín, Colombia}
\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item Built backend solutions with Python (Django) and frontend with React.
    \item Led development of blockchain and data analytics solutions.
    \item Managed cloud infrastructure on AWS, GCP, and IBM Cloud.
\end{itemize}

\resumeSubheading
{Professor}{Jan 2010 -- Oct 2021}
{Universidad de Antioquia}{Medellín, Colombia}
\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item Taught Machine Learning and Data Science courses using Python, NumPy, Pandas, TensorFlow, and PyTorch.
    \item Mentored research projects and developed curriculum for mathematics and ML.
\end{itemize}
\end{itemize}

\section{Featured Projects}
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item \textbf{\href{https://github.com/Monadical-SAS/Morpheus}{Morpheus -- AI Image Generation Platform \normalfaExternalLink}}
    \begin{itemize}[itemsep=0pt]
        \item Full-stack open-source platform for AI image generation using Python, React, and stable diffusion models. Implemented RESTful APIs, ML model integrations, and cloud infrastructure with Docker and AWS.
    \end{itemize}
    \item \textbf{\href{https://github.com/asanchezyali/ai-avatar}{Zippy -- Interactive AI Avatar \normalfaExternalLink}}
    \begin{itemize}[itemsep=0pt]
        \item Built a Next.js-based talking avatar integrating OpenAI API and Azure Cognitive Services. Developed TTS synthesis and seamless backend-frontend integration in Python and TypeScript.
    \end{itemize}
    \item \textbf{\href{https://github.com/asanchezyali/talking-avatar-with-ai}{Digital Human -- Interactive AI Avatar \normalfaExternalLink}}
    \begin{itemize}[itemsep=0pt]
        \item Engineered a conversational AI system with OpenAI GPT, Whisper, and Eleven Labs. Implemented real-time data processing and lip synchronization.
    \end{itemize}
\end{itemize}

\section{Technical Writing}
\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item \textbf{\href{https://www.asanchezyali.com/blog/en/ai/20240917ZeroShot}{Zero-Shot Text Classification}} (Sep 2024)
    \item \textbf{\href{https://www.asanchezyali.com/blog/en/differentiable-programming/20240923DifferentiablePrograms}{Neural Networks as DAGs of Parameterized Computational Programs}} (Aug 2024)
    \item \textbf{\href{https://www.asanchezyali.com/blog/en/ai-avatars/20240703DigitalHuman}{Revolutionizing Animation: Building Digital Humans with LLMs}} (Jul 2024)
    \item \href{https://www.asanchezyali.com/}{View more articles \normalfaExternalLink}
\end{itemize}

\section{Conference Talks}
\begin{itemize}[leftmargin=*]
    \item \textbf{\href{https://www.youtube.com/watch?v=m4hP1soE414}{Scaling Learning Models: Parallelism Strategies in JAX with Flax -- PyCon \normalfaYoutube}} (2024)
    \begin{itemize}[itemsep=0pt]
        \item Presented strategies for scaling machine learning models using JAX and Flax
        \item Discussed parallel computing techniques for efficient model training
    \end{itemize}
\end{itemize}

\section{Education}
\begin{itemize}[leftmargin=0pt, itemindent=0pt, label={}]
\resumeSubheading
{Master in Mathematics}{Aug 2010 - Sep 2013}
{Universidad de Antioquia}{Medellín, Colombia}

\resumeSubheading
{B.Sc. in Teaching Mathematics and Physics}{Jan 2004 - Oct 2009}
{Universidad de Antioquia}{Medellín, Colombia}
\end{itemize}

\end{document} 