\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{linkcolor}{HTML}{2b6cb0}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    urlcolor=linkcolor,
}

\begin{document}
\begin{letter}{}
\opening{Dear Hiring Team,}

I am writing to express my strong interest in the Full Stack Developer position, with a particular emphasis on my expertise in AI and machine learning integration. With over 5 years of experience in software development and a deep background in AI technologies, I bring a unique blend of technical skills and innovative problem-solving capabilities.

My professional journey has been deeply rooted in advanced AI technologies, as evidenced by my extensive work in machine learning and AI integration. At Monadical, I specialized in building and integrating AI services for information retrieval using large language models, demonstrating my ability to leverage cutting-edge AI technologies to solve complex business challenges. My technical stack in AI/ML is comprehensive, including:

\begin{itemize}
    \item Advanced AI Integration: Expertise with LangChain, LangGraph, and ScrapeGraph
    \item Machine Learning Frameworks: TensorFlow, PyTorch, and Whisper
    \item Large Language Model (LLM) Applications: Designing and implementing AI-powered solutions
    \item Natural Language Processing: Zero-shot text classification and advanced NLP techniques
\end{itemize}

My featured projects further highlight my AI expertise:

1. Morpheus - AI Image Generation Platform: I contributed to an open-source platform that leverages stable diffusion models, showcasing my ability to implement complex AI technologies in full-stack applications.

2. Interactive AI Avatars (Zippy and Digital Human): These projects demonstrate my skill in creating sophisticated AI systems that integrate OpenAI's language models, Azure Cognitive Services, and advanced speech synthesis technologies.

My academic background as a Professor at Universidad de Antioquia, where I taught advanced Machine Learning courses, has given me a strong theoretical foundation in AI technologies. I've mentored research projects in Category Theory and ML applications, bringing a deep analytical approach to AI development.

My technical writing further underscores my AI expertise, with published articles on topics such as:
- Zero-Shot Text Classification
- Neural Networks as Differentiable Programming
- Building Digital Humans with Large Language Models

Additionally, my conference talk at PyCon 2024 on "Scaling Learning Models: Parallelism Strategies in JAX with Flax" demonstrates my commitment to advanced AI and machine learning technologies.

I am particularly excited about the opportunity to bring my AI integration skills to your team, combining full-stack development expertise with cutting-edge artificial intelligence technologies. My ability to bridge theoretical knowledge with practical implementation makes me uniquely positioned to contribute to innovative AI-driven solutions.

I would welcome the opportunity to discuss how my skills and experience can contribute to your team's success in developing advanced technological solutions.

\closing{Sincerely,}

\vspace{12pt}
Alejandro Sánchez Yalí\\
Full Stack Software Engineer | AI/ML\\
\href{mailto:asanchezyali@gmail.com}{asanchezyali@gmail.com}\\
\href{https://www.linkedin.com/in/asanchezyali}{LinkedIn: asanchezyali}\\
\href{https://asanchezyali.com}{asanchezyali.com}\\
\href{https://cal.com/asanchezyali/full-time-opportunities}{Calendar: Let's Connect}
\end{letter}
\end{document}