\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\definecolor{linkcolor}{HTML}{2b6cb0}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    urlcolor=linkcolor,
}
\begin{document}
\begin{letter}{}
\opening{Dear Hiring Team,}

I am writing to express my interest in the Full Stack Developer position at your company. With over 5 years of experience in creating robust and efficient solutions across frontend and backend applications, I believe my technical skills and experience align perfectly with the requirements outlined in your job posting.

During my time at Monadical, I developed and maintained full-stack applications using Python, Django, and React with a focus on scalable architectures—skills that directly match your requirements for RESTful API design and implementation. I also built and integrated AI services for information retrieval using large language models, demonstrating my ability to work with emerging technologies.

My technical expertise includes:
\begin{itemize}
\item Proficiency in JavaScript, Python, HTML5, and CSS3
\item Experience with React and Next.js frontend frameworks
\item Expertise in Django and Flask backend frameworks 
\item Knowledge of PostgreSQL and MongoDB databases
\item Experience with Docker, Git, and development workflows
\end{itemize}

Beyond technical skills, my background as a mathematics professor at Universidad de Antioquia has strengthened my analytical thinking and communication abilities—qualities that enable me to translate business strategy into technical solutions as mentioned in your job requirements. I pride myself on my creativity, attention to detail, and ability to adapt to changing environments.

In collaborative projects like Morpheus, I contributed to building a full-stack open-source platform for AI image generation, implementing RESTful APIs and developing scalable infrastructure using Docker and AWS services. This experience demonstrates my capability to analyze complex business challenges and identify opportunities for growth.

I am particularly excited about this remote opportunity based in Colombia, as it would allow me to contribute to transforming ideas into reality through technology while maintaining my connection to the local tech ecosystem.

I would welcome the opportunity to discuss how my experience and skills could contribute to your team's success. Thank you for considering my application.

\closing{Sincerely,}

\vspace{12pt}
Alejandro Sánchez Yalí\\
Full Stack Software Developer | AI/ML\\
\href{mailto:asanchezyali@gmail.com}{asanchezyali@gmail.com}\\
\href{https://www.linkedin.com/in/asanchezyali}{LinkedIn: asanchezyali}\\
\href{https://asanchezyali.com}{asanchezyali.com}\\
\href{https://cal.com/asanchezyali/full-time-opportunities}{Calendar: Let's Connect}
\end{letter}
\end{document}